Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-16 doc/PRF2022/PRF_main.tex
updates

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{Fig2a.png}
  \includegraphics[width=0.4\textwidth]{Fig2b.png}\\
  \includegraphics[width=0.4\textwidth]{Fig2c.png}
  \includegraphics[width=0.4\textwidth]{Fig2d.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structure. In order to expedite the self-assembly procedure, all particles are placed in a $8\times8$ box initially. (b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively. Colors represent the boundary values that increases from minimum (blue) to maximum (red).  Panel (b) reaches the equilibrium at $t=1200$; Panel (c) reaches the steady-state at $t=600$; Panel (d) reaches the final state at $t=180$.}
\end{figure}

@@

The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow. After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(c) in a shear flow when $\dot\gamma=0.15$. }
\end{figure}

@@

Here are demonstrations of having JP vesical and multi-lamellar structure in a narrow channel 
under a shear flow.
Simulation results and snapshot are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles. Both starting configurations are relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.

>>>>

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{Fig2a.png}
  \includegraphics[width=0.4\textwidth]{Fig2b.png}\\
  \includegraphics[width=0.4\textwidth]{Fig2c.png}
  \includegraphics[width=0.4\textwidth]{Fig2d.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:relax} (a) Initial configuration for $N_b=60$ structures. In order to expedite the self-assembly procedure, all particles are placed in a $8\times8$ box initially. (b)--(d) Equilibruim states for all boundary conditions~\eqref{eq:bcs}(i)--(iii), respectively. Colors represent the boundary values that increases from minimum (blue) to maximum (red).  Panel (b) reaches the equilibrium at $t=1200$; Panel (c) reaches the steady-state at $t=600$; Panel (d) reaches the final state at $t=180$.}
\end{figure}

@@

The second set of simulation is putting the equilibrium state of the boundary condition \eqref{eq:bcs} (iii), the checker board, in a shear flow. After a set of empirical numerical investigations, we obtain a critical shear rate $\dot\gamma=0.15$ where the checker board deforms into stripes and small groups of JP. Figure~\ref{fig:shear_2}(a)--(d) show configurations when $t=\{0,50,100,150\}$. %The deformation starts with stripe separations
%
\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{shear_checker_0.png}
  \includegraphics[width=0.4\textwidth]{shear_checker_250.png}\\
  \includegraphics[width=0.4\textwidth]{shear_checker_500.png}
    \includegraphics[width=0.4\textwidth]{shear_checker_750.png}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:shear_2} Snapshots of simulation using boundary condition \eqref{eq:bcs}(iii) in a shear flow when $\dot\gamma=0.15$. }
\end{figure}

@@

Here are demonstrations of having JP vesicle and multi-lamellar structure in a narrow channel 
under a shear flow.
Simulation results and snapshots are shown in Figures~\ref{fig:confined_vesicle} and Figure~\ref{fig:confined_lamellar} where the JP vesicle has $N_b=25$ particles and JP lamellar has $N_b=40$ particles, respectively. Both starting configurations are pre-relaxed and the channel width in the narrow part is about 5 length units in the vesicle case and 4 length units in the lamellar case.
